Modeling the Latent Space of Symbolic String Quartet Music

### 2021-06-07 papers/final/alex/paper.tex
paper edits

Data augmentation was also tested--\cite{oore_this_2018} suggests
augmentation via pitch shifting each training example up or down by up
to six semitones in order to create additional training examples and
reduce overfitting, so we followed that recommendation and used it to
double the size of the training dataset. As a result, we saw much
lower validation losses (compare Figure \ref{loss} and Figure
\ref{loss_augment} and a small but noticeable improvement in the
fidelity of the song reconstructions, suggesting that this method was
effective in reducing overfitting.

@@

A collection of samples of the autoencoded outputs and interpolations,
converted to mp3 format, is presented at the following URL:
\url{https://drive.google.com/drive/folders/1SlQOI_cL452PftO3KmOYO_qglE2RotCX?usp=sharing}.
Each of the 18 directories contains five interpolations between two of
the string quartet pieces in the MusicNet corpus, numbered 0-4, where
0 is the reconstruction of the first piece, 4 is the reconstruciton of
the second piece, and 1-3 are linear interpolations between the two
pieces. Each file is cropped to the first 16 measures only.

@@

\begin{itemize}
\tightlist
\item \texttt{Haydn/2104\_op64n5\_1.mid} and \texttt{Ravel/2178\_gr\_rqtf2.mid}
\item \texttt{Haydn/2105\_op64n5\_2.mid} and   \texttt{Ravel/2179\_gr\_rqtf3.mid}
\item \texttt{Haydn/2106\_op64n5\_3.mid} and   \texttt{Ravel/2177\_gr\_rqtf1.mid}
\item \texttt{Beethoven/2497\_qt11\_4.mid} and \texttt{Mozart/1822\_kv\_421\_1.mid}
\item \texttt{Beethoven/2433\_qt16\_3.mid} and \texttt{Mozart/1859\_kv\_464\_2.mid}
\item \texttt{Beethoven/2368\_qt12\_4.mid} and \texttt{Mozart/1807\_kv\_387\_3.mid}
\item \texttt{Beethoven/2314\_qt15\_2.mid} and \texttt{Mozart/1791\_kv\_465\_4.mid}
\item \texttt{Beethoven/2480\_qt05\_1.mid} and \texttt{Mozart/1792\_kv\_465\_1.mid}
\item \texttt{Beethoven/2481\_qt05\_2.mid} and \texttt{Mozart/1835\_kv\_590\_3.mid}
\item \texttt{Beethoven/2379\_qt08\_4.mid} and \texttt{Mozart/1805\_kv\_387\_1.mid}
\item \texttt{Beethoven/2365\_qt12\_1.mid} and \texttt{Mozart/1793\_kv\_465\_2.mid}
\item \texttt{Beethoven/2562\_qt02\_4.mid} and \texttt{Mozart/1790\_kv\_465\_3.mid}
\item \texttt{Beethoven/2494\_qt11\_1.mid} and \texttt{Mozart/1789\_kv\_465\_2.mid}
\item \texttt{Beethoven/2403\_qt01\_4.mid} and \texttt{Mozart/1788\_kv\_465\_1.mid}
\item \texttt{Beethoven/2376\_qt08\_1.mid} and \texttt{Dvorak/1916\_dvq10m1.mid}
\item \texttt{Beethoven/2384\_qt13\_4.mid} and \texttt{Bach/2242\_vs1\_2.mid}
\item \texttt{Beethoven/2560\_qt02\_2.mid} and \texttt{Beethoven/2621\_qt07\_1.mid}
\item \texttt{Beethoven/2377\_qt08\_2.mid} and \texttt{Beethoven/2381\_qt13\_1.mid}
\end{itemize}

>>>>

Data augmentation was also tested--Oore et al (2018)
\cite{oore_this_2018} suggests augmentation via pitch shifting each
training example up or down by up to six semitones in order to create
additional training examples and reduce overfitting, so we followed
that recommendation and used it to double the size of the training
dataset. As a result, we saw much lower validation losses (compare
Figure \ref{loss} and Figure \ref{loss_augment} and a small but
noticeable improvement in the fidelity of the song reconstructions,
suggesting that this method was effective in reducing overfitting.

@@

A collection of samples of the autoencoded outputs and interpolations,
converted to mp3 format, is presented at the following URL:
\url{https://drive.google.com/drive/folders/1SlQOI_cL452PftO3KmOYO_qglE2RotCX?usp=sharing}.
Each of the 18 directories contains five interpolations between two of
the string quartet pieces in the MusicNet corpus, numbered 0-4, where
0 is the reconstruction of the first piece, 4 is the reconstruction of
the second piece, and 1-3 are linear interpolations between the two
pieces. Each file is cropped to the first 16 measures only.

@@

\begin{itemize}
\tightlist
\item \texttt{Haydn/2104\_op64n5\_1.mid} , \texttt{Ravel/2178\_gr\_rqtf2.mid}
\item \texttt{Haydn/2105\_op64n5\_2.mid} ,   \texttt{Ravel/2179\_gr\_rqtf3.mid}
\item \texttt{Haydn/2106\_op64n5\_3.mid} ,   \texttt{Ravel/2177\_gr\_rqtf1.mid}
\item \texttt{Beethoven/2497\_qt11\_4.mid} , \texttt{Mozart/1822\_kv\_421\_1.mid}
\item \texttt{Beethoven/2433\_qt16\_3.mid} , \texttt{Mozart/1859\_kv\_464\_2.mid}
\item \texttt{Beethoven/2368\_qt12\_4.mid} , \texttt{Mozart/1807\_kv\_387\_3.mid}
\item \texttt{Beethoven/2314\_qt15\_2.mid} , \texttt{Mozart/1791\_kv\_465\_4.mid}
\item \texttt{Beethoven/2480\_qt05\_1.mid} , \texttt{Mozart/1792\_kv\_465\_1.mid}
\item \texttt{Beethoven/2481\_qt05\_2.mid} , \texttt{Mozart/1835\_kv\_590\_3.mid}
\item \texttt{Beethoven/2379\_qt08\_4.mid} , \texttt{Mozart/1805\_kv\_387\_1.mid}
\item \texttt{Beethoven/2365\_qt12\_1.mid} , \texttt{Mozart/1793\_kv\_465\_2.mid}
\item \texttt{Beethoven/2562\_qt02\_4.mid} , \texttt{Mozart/1790\_kv\_465\_3.mid}
\item \texttt{Beethoven/2494\_qt11\_1.mid} , \texttt{Mozart/1789\_kv\_465\_2.mid}
\item \texttt{Beethoven/2403\_qt01\_4.mid} , \texttt{Mozart/1788\_kv\_465\_1.mid}
\item \texttt{Beethoven/2376\_qt08\_1.mid} , \texttt{Dvorak/1916\_dvq10m1.mid}
\item \texttt{Beethoven/2384\_qt13\_4.mid} , \texttt{Bach/2242\_vs1\_2.mid}
\item \texttt{Beethoven/2560\_qt02\_2.mid} , \texttt{Beethoven/2621\_qt07\_1.mid}
\item \texttt{Beethoven/2377\_qt08\_2.mid} , \texttt{Beethoven/2381\_qt13\_1.mid}
\end{itemize}
